### 2025-04-10 chapters/conclusion.tex
T-1 day to initial submission, nearly complete draft up to citations and small comments.
Final changes to main files for first draft

\epigraph{
    \textit{Wir m\"ussen wissen -- wir werden wissen}.
    %
    [We must know -- we will know.]
}{
    \href{smith-at-sfsu.net/Documents/HilbertRadio/HilbertRadio.mp3}{David Hilbert, in response}
}

@@

It has been a privilege to explore the universe with you.
%
Our goal has been to develop realistic tools for the study of the most fundamental features of our universe that humanity has been able to experimentally probe.
%
Our method was to develop collider observables whose behavior illuminates the structure of \gls{qcd} even through the obfuscating haze of contamination generated both by theoretical and experimental effects.
%
As stated by Andrew Larkoski, ``the art of jet substructure... is in the construction of observables'' \cite{}.
%
With the impressionist exposition and few new brush strokes presented in this thesis, we hope we have been able to share our sincere appreciation of the arts of jet substructure and quantum field theory.
%
A more precise understanding of the tools we presented here will require further, finer brush strokes:
%
precision calculations, experimental measurements, the modelling of theoretical and experimental uncertainties, and beyond.
%
But those tales are for another day, and another teller.

>>>>

\epigraph{
    \textit{Wir m\"ussen wissen -- wir werden wissen}.

    [We must know -- we will know.]
}{
    \href{smith-at-sfsu.net/Documents/HilbertRadio/HilbertRadio.mp3}{David Hilbert, in response}
}

@@

It has been a privilege to explore the universe with you.
%
Our goal has been to develop realistic tools for the study of the most fundamental features of our universe that humanity has been able to experimentally probe.
%
Our method was to develop collider observables whose behavior illuminates the utructure of \gls{qcd} even through the obfuscating haze of contamination generated both by theoretical and experimental effects.
%
As stated by Andrew Larkoski, ``the art of jet substructure... is in the construction of observables'' \cite{Larkoski:2024uoc}.
%
With the impressionist exposition and few new brush strokes presented in this thesis, we hope we have been able to share our sincere appreciation of the arts of jet substructure and quantum field theory.
%
A more precise understanding of the tools we presented here will require further, finer brushwork:
%
precision calculations, experimental measurements, the modelling of theoretical and experimental uncertainties, and beyond.
%
But those tales are for another day, and another teller.

### 2025-04-10 frontmatter/acknowledgements.tex
Final changes to main files for first draft

I would also like to thank Iain Stewart and Christoph Paus.
%
They are members of my thesis committee, and I am grateful for their time and effort on my behalf, but I am most grateful for the environment they created at MIT through their presence.
%
They always had a kind smile to wear, a warm comment to make, or a laugh to share.
%
I knew I could always go to Iain with any question or concern and receive a listening ear and some sound advice.
%
I knew that I could always share a joke and a lighthearted chuckle with Christoph.

On the topic of environment, I would finally like to thank Daniel Harlow.
%
\sam{}

@@

My godparents
%
My godsister
%
Last but not least, my godbrother

I also have the best siblings I could ever hope not to be related to.
%
Noah Mihelic (with credit and gratitude to my adopted family: ), who I knew before I had memories, has given me clarity, critical reasoning, incredible companionship, and many magical adventures.
%
David Rower (with credit and gratitude to my adopted family: Rachel Goldberg, Tobin Rower, Nathan Rower, and Lamia Ateshian)
%
J Rogers
%
Neeraj Tata

Sean Benevedes
%
Rikab Gambhir

@@

Liam Bradley
%
Daniel Kreizberg
%
Nate Gardner
%
Kyreija Lamothe
%
Vince Fleming
%
Ryan Croy
%
Rose
%
Erin Neitzel
%
Jason Georgis
%
Johannes Klein
%
Nicholas Maguid
%
Nathan Everett and Lubah

James Ehrets
(his parents)
%
Nick O'Dea
%
David Newsom
%
Jasmin Kwak
%
Ben Siegel
%
Dolev Bluvstein
%
Anoop Praturu
%
Ryan Stuart
%
Marvin Qi
%
Kai Goh
%
Eugene Ma
%
Brandon Louie
%
other breakers?
%
Alvin Ong
%
Yurim Lee

Zhiquan Sun, who taught me that a happy life means eating well.
%
Shankar Balasubramanian
%
Margarita Davydova
%
Atakan Firat, who never backs down from a fight.
%
Anjie Gao, who taught me (among other things) the wisdom that ``nothing is trivial''.
%
Patrick Oare, Wenzer Qin, Artur Avkadiev
%
Nick Kamp, Caolan John
%
Ouail Kitouni

Dimitra Pefkou
%
Asmund Folkestad
%
Yitian Sun
%
Gregory Ridgeway
%
Jamison Sloan
%
Sarah Geller
%
Robert Jones
%
Anita Budhraja

Lisa Yang, whose constant drive for self-improvement is always inspiring
%
Marianne Moore, Manu Srivasta
%
Joshua Lin
%
Sarah M
%
George
%
Miguel

Jasper Pont, whose free a

>>>>

I would also like to thank Iain Stewart and Christoph Paus.
%
They are members of my thesis committee, and I am grateful for their time and effort on my behalf, but I am most grateful for the environment they created at MIT through their presence.
%
They always had a warm comment to make or a laugh to share.
%
I knew I could always go to Iain with any question or concern and receive a listening ear and some sound advice.
%
I knew that I could always share a joke and a lighthearted chuckle with Christoph.

On the topic of environment, I would finally like to thank Daniel Harlow, who always had time to give a smile, kind words, and guidance in physics or beyond.

@@

My godparents Pieter and Martha van der Mersch, and my godsiblings Anna and Stephan, have provided my life with incredible warmth, amazing memories, and more empathy and useful guidance than I could have ever hoped for.

I also have the best siblings I could ever hope not to be related to.
%
Noah Mihelic (with credit and gratitude to my adopted family: Adrienne, Mark, and Josh Mihelic), who I knew before I had memories, has given me clarity, critical reasoning, incredible companionship, and many magical adventures.
%
David Rower (with credit and gratitude to my adopted family: Rachel Goldberg, Tobin Rower, Nathan Rower, and Lamia Ateshian) is funny, creative, and intelligent beyond words.
%
He has taught me countless invaluable lessons about being a clear and kind human being.
%
To say that his infectious positivity has changed my life is an understatement.
%
J Rogers is always, \textit{always} there when I need them, and whose incredible clarity and kindness is something I aspire to and benefit from every day.
%
Neeraj Tata, my hobbit-in-crime, has an incredible (and intentionally trained) ability of using sharp awareness and tolerance of all things to see what is really important in this life.

My academic siblings have also been important parts of my journey, and have taught me and been with me through both trials and tribulations.
%
Sean Benevedes, who I have known since my time at UCSB, carries with him an intelligence, humor, and empathy that make world a measurably better place.
%
I have also benefited from many useful conversations with Rikab Gambhir, whose funny jokes, intelligence, and unimpeachable sense of academic adventure have made my experience at MIT much more interesting.
%
Last but not least, Cari Cesarotti is a hilarious, high-powered, creative scientist who I love to watch playing the game of science and winning.

@@

I want to thank some of my first and most long lasting friends:
%
Liam Bradley, Daniel Kreizberg, Nate Gardner, Kyreija Lamothe, Vince Fleming, Ryan Croy.
%
Also there to support me during many formative moments were Rose Gordon, Erin Neitzel, Jason Georgis, Johannes Klein, and especially Nicholas Maguid.

More of my academic family from UCSB who have had an incredible positive influence on my life are James Ehrets (I have learned and gained so much from his openness and adventurousness, empathy, and many long conversations), Nicholas O'Dea (who perhaps belongs in my ``mentor'' section: he has shaped my entire attitude towards learning and rigor), David Newsom (he knows the many odd and memorable adventures we have shared together -- what an incredible and interesting life), Jasmin Kwak (who is an unshakeable source of support whenever I need her), Ben Siegel (whose gentle kindness I always aspire to), Dolev Bluvstein (who is a damn superhuman -- I don't know how he does it, but I feel so lucky to learn from his incredible positivity and brilliant approach to all of life), Anoop Praturu, Ryan Stuart, and Marvin Qi.
%
My b-boy crew, including Kai Goh, Eugene Ma, Brandon Louie, and Alvin Ong have given me many adventures as well, along with companionship, growth, a beautiful and positive environment for my studies, and the incredible gift of \emph{art}.
%
Last, and perhaps most important, is Yurim Lee, who gave me so much kindness, supported me through

At MIT, I was lucky enough to meet even more incredible and brilliant people.
%
I'm very grateful to Zhiquan Sun, who taught me among many wonderful lessons that a happy life means eating well.
%
Another close friend is Christopher McNally, who is open to anything, saved my life in the wilderness on one occasion, and saved my spirit in and out of the halls of MIT many more.
%
Some of my first friends at MIT were Atakan Firat (a tireless dynamo of intellect and creativity who never backs down from a fight), Ouail Kitouni (humble beyond belief, whose openness and kindness are only emphasized by his incredible knowledge, curiosity, and problem-solving ability), Shankar Balasubramanian (a pure genius, plain and simple, always with time to teach, share a problem, or give advice), Margarita Davydova (a kind, creative, brilliant theorist who makes science as beautiful as art), Ali Ghorashi (always with support and empathy to share), and Anjie Gao (who taught me, among other things, the wisdom that ``nothing is trivial'').
%
Though it took one more semester, I soon met Patrick Oare, Wenzer Qin, Artur Avkadiev -- my moral support group -- who have since been my people:
%
my confidants, my comrades-in-arms, my rocks.
%
Nick Kamp and Caolan John also deserve a special mention here;
%
they bring positivity and curiosity into every room, and every room is better for their presence.
%
Nathan Everett (my platonic soul mate) and Lubah Lerner (his soul mate) have also been close friends and wonderful sources of joy and support.
%
I have been lucky enough to learn from and share time with Dimitra Pefkou, \r{A}smund Folkestad, Gregory Ridgway, Joshua Lin, Yitian Sun, Sarah Geller, Jamison Sloan, Robert Jones, Manu Srivastava, and Ankita Budhraja.
%
I especially want to thank Lisa Yang, whose constant drive for self-improvement is continually inspiring.

The entirety of the Engineering Quantum Systems (EQuS) ``chill team'' deserves a special mention for the joy they have brought to my life:
%
Sarah Muschinske, Miguel and Lean\'or Moreira, Jorge Marques, and Andreia Allen -- and also to Will Oliver, whose incredible positive and guiding influence has brought these wonderful, brilliant people together.  % TODO: fix Leanor if necessary
%
David Rower, Lamia Ateshian, and Dolev Bluvstein deserve more thanks here as well, and Marcin Kalinowski should be thanked three times (once for his wonderful personality, twice for his incredible science, and three times for his enormous muscles, which count as another person on their own).

Finally, I remember Jasper Pont, whose ringing laugh and free spirit still float through the world.

### 2025-04-10 frontmatter/notation.tex
Final changes to main files for first draft

\begin{sambox}{Some TODOs for Sam}{}
    \begin{itemize}
        \item
            Need to fix header on problem pages, which simply use the most recent appendix instead.

        \item
            Add epsilon UV/IR calculations involving EEC

        \item
            Unify notation of epigraphs, probably want names then titles
    \end{itemize}
\end{sambox}

Here is some common notation used throughout this thesis.

\begin{itemize}
    \item
        \(A := B\) means ``\(A\) is defined to mean \(B\)'', as does \(B =: A\);

    \item
        For notational simplicity, I will set the physical constants \(\hbar = c = 1\) in all printed equations;

    \item
        We make the unfortunate choice to use the ``mostly-minus'' metric, \(g^{\mu\nu} = \text{diag}\le(+,\,-,\,-,\,-\ri)\), with the gamma matrix algebra \(\acomm{\gamma^\mu}{\gamma^\nu} = 2 g^{\mu\nu}\,.\).

@@

    \item
        \sam{LO, NLO, LL, NLL, etc.}

    \item
        The \textit{energy fraction} carried by a particular particle in a scattering event or jet, relative to the total energy of the event or jet, will play an important role in this thesis.
        %
        We will use the symbol \(z_i\) to denote the energy fraction particle \(i\) relative to a ``parent'' of any type, such as a pair of particles, a jet, or an entire event (which of these should be clear based on context):
        \begin{align}
            z_i
            \eqdelta
            \frac{E_i}{E_\text{tot}}
            \,.
        \end{align}

    \item
        We will also use the following standard definitions:
        \begin{subequations}
        \label{eq:qcd_coupling}
        \begin{align}
            \label{eq:as_defn}
            \as &= \frac{\alpha_s}{4\pi}
            \\
            \label{eq:beta_fn_defn}
            \frac{\dd}{\dd\log\mu}\alpha_s(\mu)
            &\eqdelta
            \beta(\alpha_s)
            =
            -2\beta_0 \alpha_s(\mu)^2 + \mathcal{O}\le(\alpha_s(\mu)^3\ri)
            \\
            \label{eq:alphas_1loop}
            \alpha_s^\text{(1-loop)}(\mu)
            &=
            \frac{\alpha_s(Q)}{1 + 2\alpha_s(Q) \beta_0 \log(\frac{\mu}{Q})}
            ,
        \end{align}
        where
        \begin{align}
            \beta_0 = \frac{1}{12\pi}\le(11\,C_A - 4\,T_f n_f\ri)
        \end{align}
        \end{subequations}
        is the leading coefficient of the QCD beta function, \(n_f = 5\) denotes the number of effectively massless quark flavors, \(Q\) indicates a reference scale (such as the energy scale of a hard process), and
        \begin{subequations}
        \label{eq:group_theory}
        \begin{align}
            C_F &= \frac{N_c^2 - 1}{2N_c}
            \xrightarrow[]{\text{QCD}}
            \frac{4}{3}
            \\
            C_A &= N_c
            \xrightarrow[]{\text{QCD}}
            3
            \\
            T_F &= \frac{1}{2}
            ,
        \end{align}
        \end{subequations}
        denote the quadratic Casimir for the fundamental representation of \(SU(N_c)\), the quadratic Casimir for the adjoint representation, and the Dynkin index of the fundamental representation, respectively.
        %
        The expressions of \Eq{group_theory} are often referred to collectively as \textit{group theory factors}.
        %
        For QCD, \(N_c = 3\), \(C_F = 4/3\), and \(C_A = 3\), giving \(
            \beta_0 = \le(11 - 2 n_f / 3\ri)/4\pi
            .
        \)
\end{itemize}

>>>>

Here is some common notation used throughout this thesis.
\begin{itemize}
    \item
        \(A := B\) means ``\(A\) is defined to mean \(B\)'', as does \(B =: A\);

    \item
        For simplicity, I set the physical constants \(\hbar = c = 1\) in all printed equations;

    \item
        We make the unfortunate choice to use the ``mostly-minus'' metric, \(g^{\mu\nu} = \text{diag}\le(+,\,-,\,-,\,-\ri)\), such that \(\acomm{\gamma^\mu}{\gamma^\nu} = 2 g^{\mu\nu}\), and with the saving grace that we can write \(p^2 = m^2\).

    \item
        We will use the symbol \(z_i\) to denote the energy fraction particle \(i\) relative to a ``parent'' of any type, such as a pair of particles, a jet, or an entire event (which of these should be clear based on context):
        \begin{align}
            z_i
            \eqdelta
            \frac{E_i}{E_\text{tot}}
            \,.
        \end{align}

    \item
        We will also use the following standard definitions:%
        \footnote{
            We are leaving out the term \(-\epsilon \alpha_s\) that appears in \(d=4-2\epsilon\) dimensions when defining \(\alpha_s\) to be dimensionless.
            %
            The extra factor of two in the beta function vanishes if one defines the beta function instead to be the derivative of \(\alpha_s\) relative to \(\ln\mu^2\), or if it is written in terms of \(g_s\):
            %
            \(\dd g_s / \dd\ln_\mu = - g_s \sum_n \beta_n \le(\alpha_s/4\pi\ri)^{n+1}\).
        }
        \begin{subequations}
        \label{eq:qcd_coupling}
        \begin{align}
            \label{eq:as_defn}
            \alpha_s = \frac{g^2_s}{4\pi}
            \,,&
            \qquad\quad
            \as = \frac{\alpha_s}{4\pi}
            \,,
            \\
            \label{eq:beta_fn_defn}
            \beta(\alpha_s)
            :=
            \frac{\dd}{\dd\log\mu}\alpha_s&(\mu)
            =
            -2 \, \alpha_s
            \sum_{n=0}^\infty
            \beta_n \le(\frac{\alpha_s}{4\pi}\ri)^{n+1}
            \,.
        \end{align}
        At one loop (i.e. ignoring \(\beta_m\) for \(m \geq 1\)),
        \begin{align}
            \label{eq:alphas_1loop}
            \alpha_s^\text{(1-loop)}(\mu)
            &=
            \frac{\alpha_s(Q)}{1 + \alpha_s(Q) \beta_0 \log(\mu/Q)/2\pi}
            \,.
        \end{align}
        where
        \begin{align}
            \beta_0 = \frac{11}{3}\,C_A - \frac{4}{3}\,T_f N_f
        \end{align}
        \end{subequations}
        is the leading coefficient of the QCD beta function, \(N_f\) denotes the number of effectively massless quark flavors (\(N_f = 5\) in this thesis), \(Q\) indicates a reference scale (such as the energy scale of a hard process), and
        \begin{align}
        \label{eq:group_theory}
            C_F = \frac{N_c^2 - 1}{2N_c}
            \xrightarrow[]{\text{QCD}}
            \frac{4}{3}
            \,,
            \qquad
            C_A = N_c
            \xrightarrow[]{\text{QCD}}
            3
            \,,
            \qquad
            T_F = \frac{1}{2}
            \,,
        \end{align}
        denote the quadratic Casimir for the fundamental representation of \(SU(N_c)\), the quadratic Casimir for the adjoint representation, and the Dynkin index of the fundamental representation, respectively.
        %
        The expressions of \Eq{group_theory} are often referred to collectively as \textit{group theory factors}.
        %
        For QCD, \(N_c = 3\), \(C_F = 4/3\), and \(C_A = 3\), giving \(\beta_0 = 11 - 2 N_f / 3\,.\)

    \item
        The \glslink{splittingfn}{Dokshitzer-Gribov-Lipatov-Altarelli-Parisi (DGLAP) splitting functions}, computed in \Sec{splitting-functions} and related to the \glslink{dglapeqn}{DGLAP equation} in \Sec{p2p-fragmentation}, are often written in the \emph{exclusive} form \(P_{i\,j \leftarrow \ell}(z)\), with a probabilistic interpretation related to the probability of a parton of type \(\ell\) to split into partons of type \(i\), carrying an energy fraction \(z = z_i = E_i / E_\ell\), and type \(j\), carrying an energy fraction of \(z_j = 1-z\).
        %
        The \emph{inclusive} (meaning ``including a sum over some final state information'') DGLAP splitting functions are defined by
        \begin{align}
            \sum_{k'} P_{i\,k' \leftarrow \ell}(z) =: p_{i\leftarrow \ell}(z)
            \,.
        \end{align}

@@

\end{itemize}

### 2025-04-10 frontmatter/preface.tex
Final changes to main files for first draft

\section*{Preface}
\markboth{Preface}{}

% Include a link to the thesis template

First, and most importantly, please remember that problems are a \textit{shortcut} to understanding, not ``something extra''.
%
At least, good problems are :D
%
I've tried to select and invent some good problems for you (and if you have any comments or qualms with any of them, you should feel free to email me) that I hope are representative of
\begin{itemize}
    \item
        the story or ``flavor'' of the material;

@@

    \item
        the mathematics required to do some realistic (albeit simple) computations.\footnote{Even some numerical calcules! See \Sec{}}
\end{itemize}
%
From what I've seen and read, active learning is the quickest and only way.
%
Don't forget!

>>>>

\section*{Preface}
% \markboth{Preface}{Preface}

\epigraph{Question everything at least once.}{Mansour Alipour-fard}

\epigraph{You earn your right to speculate depending on how much work you do.}{Barton Zweibach}

The nominal goal of this thesis is to present my research from my time in graduate school.

Another goal I have is that, in a couple of (albeit concerted) weeks, you can master what took my six years to learn (to the extent that I have mastered it)!
%
First, and most importantly, please remember that problems are a \textit{shortcut} to understanding, not ``something extra''.
%
At least, good problems are.
%
I've tried to select and invent some good problems for you%
\footnote{
    And if you have any comments or qualms regarding any of them, you should feel free to email me.
}
%
that I hope are representative of
\begin{itemize}
    \item
        the story or ``flavor'' of the material;

@@

    \item
        the mathematics required to do some realistic (albeit simple) computations.
\end{itemize}
%
From what I've seen and read, active learning is the quickest and only way.
%
Don't forget!

Before we begin the thesis, I will add some clarifying comments regarding both goals.
%
First, my main contributions presented in this thesis are
\begin{itemize}
    \item
        The introduction of the \PIRANHA{} paradigm for continuous grooming, with Eric Metodiev, Patrick Komiske, and Jesse Thaler.
        %
        This research was presented in \ul{Pileup and Infrared Radiation Annihilation (PIRANHA): A Paradigm for Continuous Jet Grooming} \cite{Alipour-Fard:2023prj}.
        %
        For \PIRANHA{}, see especially \Secss{piranha}{sd_discont}{grooming-pheno};

    \item
        The development of new, efficient, and visually intuitive higher-point energy correlators -- both \emph{projected} (PENCs) and \emph{resolved} (RENCs) with Ankita Budhraja, Wouter Waalejwin, and Jesse Thaler.
        %
        This research was presented in \ul{New Angles on Energy Correlators} \cite{Alipour-fard:2024szj}.
        %
        For PENCs and RENCs, see \Sec{new-angles};

    \item
        The initiation of the study of general energy-weighted correlations, called Energy Weighted Observable Correlations (EWOCs), that are not restricted to angular correlations (e.g. as in the case of PENCs and RENCs).
        %
        This research was presented in \ul{Energy Correlators Beyond Angles} \cite{Alipour-fard:2025dvp}.
        %
        For EWOCs, see especially \Sec{ewocs}.
\end{itemize}

Second, since I attempt to provide especially clear and step-by-step derivations which highlight at least my own assumptions, several of the derivations presented in this thesis, even of fundamental concepts, are original.
%
Therefore, invoking the uncertainty principle, I advise you to watch closely for their \emph{correctness}.
%
I hope to have given enough detail to make this possible, and I encourage you to email me if I have not.

Finally, in addition to the several texts that appear in my citations below, another under-celebrated text on \glslink{qcd}{quantum chromodynamics} is \underline{Applications of Perturbative QCD}, by Richard D. Field \cite{Field:1989uq}, which pays incredible attention to detail in the presentation of calculations.
%
Of course, it would be a shame to access this book quickly, easily, and for free using \url{libgen.is}, so I will mention that it is also available (at time of writing) at \href{https://www.desy.de/~jung/qcd_and_mc_2009-2010/R.Field-Applications-of-pQCD.pdf}{this desy.de link}.

\begin{center}
Good luck.
\end{center}

### 2025-04-10 frontmatter/prerequisites.tex
Final changes to main files for first draft

\epigraph{``You earn your right to speculate depending on how much work you do.''}{Barton Zweibach}

@@

In addition, I expect that you should probably be able to understand the following pieces of physics:
\begin{itemize}
    \item
        The strong coupling \(\alpha_s(\mu)\) obeys the \vocab{renormalization group equation}
        \begin{equation}
        \mu \frac{d}{d\mu} \alpha_s(\mu) = \beta(\alpha_s(\mu))
        =
        - \sum_{n=0}^\infty \beta_n
        {\left(\frac{\alpha_s(\mu)}{4\pi}\right)}^{n+2},
        \end{equation}
        \sam{check} with the first \vocab{beta function coefficient}
        \begin{equation}
            \beta_0
            =
            \frac{1}{4\pi}\le(
                \frac{11}{3} C_A - \frac{4}{3} T_F n_f
            \ri)
            ,
        \end{equation}
        taking an important role at one-loop and in the studies in this thesis.

    \item
        The running of the strong coupling leads to a special scale by \vocab{dimensional transmutation}:
        %
        given the coupling at some scale \(\mu\), the form of the beta function indicates that the coupling becomes infinite at a scale we call \(\LambdaQCD\).
        %
        Ignoring the effects of the beta-function coefficients other than \(\beta_0\), we have
        \begin{equation}
            \LambdaQCD = \mu \exp\left(-\frac{1}{2\beta_0 \alpha_s(\mu)}\right).
        \end{equation}
        \sam{This was just written by copilot -- double check in terms of these definitions.}
\end{itemize}

@@

\textbf{Basics of Quantum Field Theory:}
\begin{itemize}
    \item
        \underline{Book name}, by \sam{author}

        This book \sam{does ...}

        Available at \sam{place/url}
\end{itemize}

@@

        This book \sam{does ...}

>>>>

% \epigraph{``You earn your right to speculate depending on how much work you do.''}{Barton Zweibach}

@@

In addition, I expect that you should probably be able to understand the following pieces of physics:
\begin{itemize}
    \item
        The strong coupling \(\alpha_s(\mu)\) obeys the \vocab{renormalization group equation}
        \begin{equation}
        \beta(\alpha_s(\mu))\mu
        :=
        \frac{d}{d\mu} \alpha_s(\mu)
        =
        -2\alpha_s\sum_{n=0}^\infty \beta_n
        {\left(\frac{\alpha_s(\mu)}{4\pi}\right)}^{n+1},
        \end{equation}
        {check} with the first \vocab{beta function coefficient}
        \begin{equation}
            \beta_0
            =
            \frac{11}{3} C_A - \frac{4}{3} T_F n_f
            \,,
        \end{equation}
        taking an important role at one-loop and in the studies in this thesis.

    \item
        The running of the strong coupling leads to a special scale by \vocab{dimensional transmutation}:
        %
        given the coupling at some scale \(\mu\), the form of the beta function indicates that the coupling becomes infinite at a scale we call \(\LambdaQCD\).
        %
        Ignoring the effects of the beta-function coefficients other than \(\beta_0\), we have
        \begin{equation}
            \LambdaQCD = \mu \exp\left(-\frac{1}{2\beta_0 \alpha_s(\mu)}\right).
        \end{equation}
        {This was just written by copilot -- double check in terms of these definitions.}
\end{itemize}

@@

\textbf{Basics of Quantum Field Theory:}
\begin{itemize}
    \item
        \underline{Book name}, by {author}

        This book {does ...}

        Available at {place/url}
\end{itemize}

@@

        This book {does ...}

### 2025-04-10 includes/glossary.tex
Final changes to main files for first draft

        \newglossaryentry{redsplitfn}
        {
          name=reduced,
          text=reduced splitting function,
          first=\vocab{reduced splitting function},
          description={
            A splitting function \(\overline{p}(z) = p(z) + p(1-z)\), with \(z \leq 1/2\), designed for calculations sensitive to the softer branch of a partonic splitting
          },
          parent=splittingfn
        }

@@

    \newglossaryentry{plus-fn}
    {
      name=plus-regularized,
      text=plus-function,
      first=\vocab{plus-regularized distribution} (or plus-function),
      description={A regularization of a parent function (a plus-function) that removes singularities and ensures integrability;
      %
      in particular, a plus-function integrates to zero},
      parent=distribution
    }

@@

\newglossaryentry{mpi}
{
  name=multiple parton interactions (MPI),
  first=\vocab{multiple parton interactions} (\vocab{MPI}),
  text=MPI,
  long=multiple parton interactions,
  short=MPI,
  description={
      A parton-level model for the underlying event of proton-proton collisions, in which UE is formed by interactions of several relatively low-energy partonic consituents of the proton.
      %
      See UE
    }
}

@@

\newglossaryentry{pileup}
{
  name=pileup (PU),
  first=\vocab{pileup} (\vocab{PU}),
  text=PU,
  long=pileup,
  short=PU,
  description={}
}

    \newglossaryentry{pu-mitigation}
    {
      name=mitigation,
      text=pileup mitigation,
      first=\vocab{pileup mitigation},
      description={},
      parent=pileup
    }

    \newglossaryentry{pusubevent}
    {
      name=pileup-subtracted event,
      text=pileup-subtracted event,
      first=\vocab{pileup subtracted event},
      description={},
      parent=pileup
    }

@@

\newglossaryentry{radiator}
{
  name=radiator,
  first=\vocab{radiator},
  description={}
}

@@

\newglossaryentry{soft-distortion}
{
  name=soft distortion,
  text=soft distortion,
  first=\vocab{soft distortion},
  description={
        A type of low-energy pollution, including hadronization and detector effects, which slightly adjusts the energies and momenta of particles, jets, and subjets
  }
}

@@

\newglossaryentry{ue}
{
  name=underlying event (UE),
  first=\vocab{underlying event} (\vocab{UE}),
  text=UE,
  long=underlying event,
  short=UE,
  description={
      A phenomenon in collisions of composite particles, in which high-energy events and jets are accompanied by a bath of relatively low-energy particles
  }
}

@@

\newglossaryentry{vetoalg}
{
    name=algorithm,
    text=veto algorithm,
    first=\vocab{veto algorithm},
    description={
        \sam{link to sudakov factor/exponent?}
    },
    parent=veto
}
\newglossaryentry{vetoreg}
{
    name=region,
    text=veto region,
    first=\vocab{veto region},
    description={
        \sam{link to radiator?}
    },
    parent=veto
}

>>>>

        \newglossaryentry{redsplitfn}
        {
          name=reduced,
          text=reduced splitting function,
          description={
            A splitting function \(\overline{p}(z) = p(z) + p(1-z)\), with \(z \leq 1/2\), designed for calculations sensitive to the softer branch of a partonic splitting
          },
          parent=splittingfn
        }

@@

    \newglossaryentry{plus-fn}
    {
      name=plus-regularized,
      text=plus-function,
      first=plus-regularized distribution (or plus-function),
      description={A regularization of a parent function (a plus-function) that removes singularities and ensures integrability;
      %
      in particular, a plus-function integrates to zero},
      parent=distribution
    }

@@

\newglossaryentry{mpi}
{
  name=multiple parton interactions (MPI),
  first=multiple parton interactions (MPI),
  text=MPI,
  long=multiple parton interactions,
  short=MPI,
  description={
      A parton-level model for the underlying event of proton-proton collisions, in which UE is formed by interactions of several relatively low-energy partonic consituents of the proton.
      %
      See UE
    }
}

@@

\newglossaryentry{pileup}
{
  name=pileup (PU),
  first=pileup (PU),
  text=PU,
  long=pileup,
  short=PU,
  description={}
}

    \newglossaryentry{pu-mitigation}
    {
      name=mitigation,
      text=pileup mitigation,
      first=pileup mitigation,
      description={},
      parent=pileup
    }

    \newglossaryentry{pusubevent}
    {
      name=pileup-subtracted event,
      text=pileup-subtracted event,
      first=pileup subtracted event,
      description={},
      parent=pileup
    }

@@

\newglossaryentry{radiator}
{
  name=radiator,
  description={}
}

@@

\newglossaryentry{soft-distortion}
{
  name=soft distortion,
  text=soft distortion,
  description={
        A type of low-energy pollution, including hadronization and detector effects, which slightly adjusts the energies and momenta of particles, jets, and subjets
  }
}

@@

\newglossaryentry{ue}
{
  name=underlying event (UE),
  first=underlying event (UE),
  text=UE,
  long=underlying event,
  short=UE,
  description={
      A phenomenon in collisions of composite particles, in which high-energy events and jets are accompanied by a bath of relatively low-energy particles
  }
}

@@

\newglossaryentry{vetoalg}
{
    name=algorithm,
    text=veto algorithm,
    description={
        \sam{link to sudakov factor/exponent?}
    },
    parent=veto
}
\newglossaryentry{vetoreg}
{
    name=region,
    text=veto region,
    description={
        \sam{link to radiator?}
    },
    parent=veto
}
